\documentclass[main.tex]{subfiles}
\begin{document}
	\begin{drama}
% 		Commander Paul Ramsey
		\Character{Commander Ramsey}{ramsey}
		
% 		Executive Officer Daniel Reynolds
% 		Sometimes ``Danny''
		\Character{Executive Officer Reynolds}{reynolds}
		
% 		Health and Safety Officer Alice Lewis
		\Character{Health and Safety Officer Lewis}{lewis}
		
% 		Crew Geologist Alexander Bates
% 		``Alex''
		\Character{Crew Geologist Bates}{bates}
		
% 		Crew Biologist Christine Morrison
		\Character{Crew Biologist Morrison}{morrison}
		
% 		Crew Engineer Harold Jones
% 		``Harry''
		\Character{Crew Engineer Jones}{jones}
		
		\Scene{Audio Log Transcript 1: Sol 24 MTC 11:26}
	
		\jonesspeaks:		Hey!  Christine!  Come check out this weird rock!
		\morrisonspeaks:	Coming.  What is it Harry?
		\jonesspeaks:		I don't know.  Shit!  That's sharp.  It poked a hole in my glove! I think it cut my finger,
		too.
		\ramseyspeaks:		Dammit Harry!  You know that we only have so many of these suits, right?  Head back to base.
		Alice, you go with him.  Everyone else, continue gathering samples.
		\jonesspeaks:		Roger that, Commander.  Heading back to base.
		\lewisspeaks:		Got it Paul.  I'll accompany him and patch him up.
		
		\Scene{Audio Log Transcript 2:  Sol 24 MTC 12:36}
		
		\lewisspeaks:		How the hell did you cut yourself up that bad, Harry?  This cut is deep.  
		\jonesspeaks:		I don't know, Alice.  I just picked up that rock, and next thing I know my glove is punctured
		and my finger is cut.  
		\lewisspeaks:		The cut's all sandy.  I'm gonna need to wash it out.  This will sting a bit.  
		\jonesspeaks:		Aghh!
		\lewisspeaks:		Sorry.  I'm gonna bandage it up now.  Try not to do this again, please?
		\jonesspeaks:		I'll try.   
		
		\Scene{Lewis Personal Log Sol 24}
	\end{drama}
		
	Today was a interesting day.  After a long morning of collecting samples to look for
	potential life in the soil, Harry picked up a strangely organic-looking rock and somehow managed to cut
	through his glove and into his finger.  I didn't even know that was possible.  I will have to check back periodically on his
	finger as it heals.  
	\begin{drama}
		\Character{Commander Ramsey}{ramsey}
		\Character{Executive Officer Reynolds}{reynolds}
		\Character{Health and Safety Officer Lewis}{lewis}
		\Character{Crew Geologist Bates}{bates}
		\Character{Crew Biologist Morrison}{morrison}
		\Character{Crew Engineer Jones}{jones}
		
		\Scene{Audio Log Transcript 3:  Sol 28 MTC 14:36}
		
		\jonesspeaks:		Alice, I'm not feeling so well.  My head is killing me, my finger is sending stabbing pains
		down my arms, and I feel super nauseous.
		\lewisspeaks:		Oh my God your face!  You're deathly pale!  Come over here quickly!  You've got an insane
		fever!  
		\ramseyspeaks:		It must be from the cut on his finger.  He's infected.  We can't take any risks.  Harry,
		we're going to have to put you in quarantine.  We absolutely cannot take the risk of the rest of the crew
		becoming infected. 
		\direct{Loud vomiting noises}
		\ramseyspeaks:		What the hell!?  You vomited all over me!  Now this room has to be decontaminated, and I
		have to be quarantined as well.  
		\ramseyspeaks:		Everyone out of the room!  Lewis and Morrison, you both go put on the biohazard suits and
		prepare to collect tissue and blood samples for analysis.  I will take care of the quarantine procedures.  
		
		\Scene{Ramsey Personal Log Sol 28}
	\end{drama}
	
	Today was pretty much the worst case scenario for discovering life on this planet.  Thank God NASA sent a
	full medical lab along with us, otherwise we would be doomed to die up here.  Morrison and Lewis are
	analyzing the blood and tissue samples from Jones and I, as well as some of the vomit and pieces of the
	original rock that started all of this.  We can only hope that they find a treatment in time, and that no one
	else is infected.  
	
	\begin{drama}
		\Scene{Morrison Personal Log Sol 28}
		
	\end{drama}
	
	We discovered life on Marse! This is the discovery of a lifetime!  Too bad it wants to kill us.  Alice and I
	will probably recieve Nobel prizes when we get back to Earth.  If we get back to Earth.  The samples from
	Harry and the Commander are processing, so Alice and I will try to get some sleep.  It has been a long,
	stressful, day.  
	
	\begin{drama}
		\Character{Commander Ramsey}{ramsey}
		\Character{Executive Officer Reynolds}{reynolds}
		\Character{Health and Safety Officer Lewis}{lewis}
		\Character{Crew Geologist Bates}{bates}
		\Character{Crew Biologist Morrison}{morrison}
		\Character{Crew Engineer Jones}{jones}
		\Scene{Audio Log Transcript 1:  Sol 29 MTC 06:15}
		
		\lewisspeaks:		Christine!  Look at this!  
		\morrisonspeaks:	This is incredible!  It's growing in the Petri dish!  It really is life!  
		\lewisspeaks:		I guess we had better get to work.  
		\morrisonspeaks:	Agreed.  We have a long day ahead of us.
		
		\Scene{Audio Log Transcript 2:  Sol 29 MTC 12:15}
		
		\ramseyspeaks:		\direct{Over intercom}  How's progress coming along?  I haven't started showing any
		symptoms yet, but Jones is getting worse.
		\lewisspeaks:		We're making progress.  Christine found out that the pathogen dies in the prescence of
		graphene.  We're working on a delivery mechanism now.  We should have a working treatment within the week. 
		\ramseyspeaks:		\direct{Over intercom}  Great work.  Keep us posted.  
		
		\Scene{Lewis Personal Log Sol 32}
	\end{drama}
	
	I've made a breakthrough.  I think I have finally figured out how this pathogen works.  The graphene
	treatment is working well in the mice, so I think it's ready for deployment to Harry and the Commander.  All
	we can do is hope that it works well enough to finally end this nightmare.  
	
	\begin{drama}
		\Scene{Ramsey Personal Log Sol 33}
	\end{drama}
	
	Lewis and Morrison delivered the working treatment to Jones and I this morning.  We can only hope it works
	as well for us as it did for the mice.  
	
	\begin{drama}
		\Scene{Ramsey Personal Log Sol 34}
	\end{drama}
	
	The treatment is working!  Jones' symptoms have lessened a bit.  His fever broke, and he finally managed to
	get some food down.  It looks like this waking nightmare is almost over.  I can't wait until we get to leave
	this planet forever.  

	\begin{drama}
		\Scene{Ramsey Personal Log Sol 38}
	\end{drama}
	
	Lewis and Morrison's tests for the pathogen have finally come back negative for Jones and I.  We can leave
	the quarantine at last.  It will be nice to stretch my legs and eat with my crew again.  I spoke with NASA on
	the radio, and they said that they are working as fast as they can to get us home as soon as possible.  Even
	though we never could have possibly anticipated this specific scenario, my crew and I knew there were risks
	to space travel.  We signed up anyway, because that's the kind of people we are.  We go where the frontier
	is, no matter how far.  
\end{document}