\documentclass[main.tex]{subfiles}
\begin{document}
\textit{Great.  Another sob story.}  I thought to myself as the woman in front of me weeped while
begging for my services.

\enquote{Listen lady.  I don't care.  Unless you have the money, I won't do it.  I don't work for free.}
I said with annoyance.  

\enquote{Paradox please!}  The woman sobbed with desperation.  \enquote{My daughter is being tortured every
waking moment by these flashbacks!  This is all of the money I have!  Please, I beg y---!}

I waved my hand and the image of the woman disappeared.  There were so many of these people nowadays. 
\textit{Why don't they understand?  I'm a dangerous cyber criminal.  I rummage around in people's
heads for a living.  I'm not a nice guy.  }  I sighed with annoyance.  Since everyone got brain-computer
interfaces, people like him became increasingly in demand.  Want to know exactly what your competitor's trade
secrets are?  Want to escape your old life completely?  Want to erase all traces of a particularly traumatic
experience?  Need to make some records disappear?  I can do all of that, and more.  If you have the money,
that is.  You can show me a live feed of a basket of puppies racing toward a cliff and I wouldn't lift a
finger until you paid me.  

Of course, most of my \enquote{services} are wildly illegal.  That's no problem for me, however.  I'm
invisible.  No law enforcement agency can touch me.  That is, if they wanted to pursue me.  I have influence
over every leader of every major law enforcement agency.  If the head of the Cyber Crimes Enforcement Division
ever wants his memories of his family back, he won't pursue me.  It's nice to be untouchable.  

I leaned back in my large and comfy computer chair, and waited for the next desperate mind to roll in.  Just
another day as the world's greatest mind hacker.  

\end{document}