\documentclass[main.tex]{subfiles}
\begin{document}

I listen to the familiar creaks and groans of my ship as I relax and settle down for another solitary dinner.
It’s been a long five months since I have talked my family back on Earth.
We normally send video messages back and forth to each other, but the latency this far out from Earth sadly makes video
calls impossible.

I suppose I should introduce myself.
My name is William, but most of my friends, the few that I have anyway, call me Bill.
I’m a space trucker.
I ship cargo to and from Mars, Earth, and Luna.
Whenever anyone on Mars breaks a water filter or needs new equipment they can’t make themselves, they have to order it
from Earth.
If they need it right away or if it’s urgent, then it can be shipped faster, but then you need to slow it down when it
gets to Mars orbit, and that uses a LOT more fuel, and therefore costs many times more per kilo than it would if it was
sent at normal speed.
As a result, people like me still have to make the long 9-month journey each way to Mars to drop off supplies and pick
up exports from the colony.
I read that Elon Musk and his company was working on automating the shipment of goods to and from Mars using some kind
of electromagnetic launcher system in Earth orbit, but his company hasn’t produced anything yet, so we still have to use
inefficient and dirty chemical rockets to get stuff around in space.

Don’t get me wrong though, I like my job.
I like that I don’t have to deal with the hustle and bustle of Earth or worry about being fired.
I just wish that someone would get around to doing something about that stupid ``No faster-than-light communication''
problem.
Depending on where I am in the trip, it can take anywhere from seconds to hours for a radio message to travel from my
ship to Earth and back.
People in the 10’s thought that a three second ping was bad, but they clearly have never tried browsing the web or
chatting with friends or relatives with a one hour ping.

Thankfully, there are other people making this journey too.
Like the Earth truckers in the 20th century, before their entire industry was automated by self-driving trucks, us space
truckers have ways of talking to each other.
While we’re still hundreds of thousands of kilometers apart, the latency is good enough that we can talk using video
chat.
Since we’re so isolated from the rest of civilization, we’ve kinda developed our own little culture.
We talk about our lives, discuss books we’ve read or TV shows we’ve watched, and gamble.
We do a lot of gambling.
While most of us prefer old school Texas hold’em, some of us prefer to play video games.

During the brief few weeks we spend on Earth or Mars when we drop off a shipment, it can be difficult to adjust back to
“civilized” society. 
It's easy to forget sometimes that “ordinary” people are obligated make small talk instead of just saying what
they mean.  
Personal hygiene is similarly easy to forget.  
Because people can’t smell you over a radio link, and deodorant is a consumable resource, us space truckers usually go without.  
I can’t even count the amount of dinner parties I’ve been kicked out of because of that.
I honestly prefer the trucker way of doing things.

\end{document}